Estimating duration in the presence of misclassification

### 2024-03-20 ATACCC.tex
clarify caption

Clear differences emerge between the vaccinated and unvaccinated groups (see \cref{ATACCC:fig:median-trajectories} and \cref{ATACCC:table:population-estimates}).
The rates of viral load increase at similar rates in the two groups, the vaccinated group have higher peak viral loads and clear the virus faster.
This leads to a shorter duration of RT-PCR positivity in the vaccinated group.
\begin{figure}
  \centering \includegraphics{ATACCC/mean_trajectories}
  \caption[Median viral load trajectories]{Trajectory (posterior median and 95\% CrI) using the median parameter values, $\exp \vec{\mu}_{\phi,g}$, excluding the within-population variation. These assume $\tau_{\max,i}=0$, however modifying this simply translates the trajectories left or right. \label{ATACCC:fig:median-trajectories}}
\end{figure}
\begin{table}
  \makebox[\linewidth]{
  \begin{tabular}{lcc}
    Parameter & Unvaccinated population & Vaccinated population \\
    Max log viral load, $\mu_{v_\text{max},g}$ & 14.9 (14.2--15.7) & 16.0 (15.2--16.8) \\
    Rate of log viral load increase, $\exp(\mu_{a,g})$ & 5.07 (3.70--7.06) & 1.25 (1.18--1.32) \\
    Rate of log viral load decrease, $\exp(\mu_{b,g})$ & 1.33 (1.09--1.63) & 1.89 (1.50--2.36) \\
  \end{tabular}
  }
  \caption{Population-level estimates of the viral load parameters (posterior medians and 95\% CrI). The vaccinated population have higher peak viral loads but clear the virus faster. \label{ATACCC:table:population-estimates}}
\end{table}

>>>>

Clear differences emerge between the vaccinated and unvaccinated groups (see \cref{ATACCC:fig:median-trajectories} and \cref{ATACCC:table:population-estimates}).
The rates of viral load increase at similar rates in the two groups, the vaccinated group have higher peak viral loads and clear the virus faster.
This leads to a shorter duration of RT-PCR positivity in the vaccinated group.
\begin{figure}
  \centering \includegraphics{ATACCC/mean_trajectories}
  \caption[Median viral load trajectories]{Trajectory (posterior median and 95\% CrI) using the population median parameter values, $\exp \vec{\mu}_{\phi,g}$, excluding the within-population variation. These assume $\tau_{\max,i}=0$, however modifying this simply translates the trajectories left or right. \label{ATACCC:fig:median-trajectories}}
\end{figure}
\begin{table}
  \makebox[\linewidth]{
  \begin{tabular}{lcc}
    Parameter & Unvaccinated population & Vaccinated population \\
    Max log viral load, $\mu_{v_\text{max},g}$ & 14.9 (14.2--15.7) & 16.0 (15.2--16.8) \\
    Rate of log viral load increase, $\exp(\mu_{a,g})$ & 5.07 (3.70--7.06) & 1.25 (1.18--1.32) \\
    Rate of log viral load decrease, $\exp(\mu_{b,g})$ & 1.33 (1.09--1.63) & 1.89 (1.50--2.36) \\
  \end{tabular}
  }
  \caption{Population-level estimates of the viral load parameters (posterior medians and 95\% CrI). The vaccinated population have higher peak viral loads but clear the virus faster. \label{ATACCC:table:population-estimates}}
\end{table}
